### 2021-03-14 article/paper_eng.tex
typo

Thus, in the process of learning, the weights of connections where pre-spikes are systematicly recieved right before the emmision of post-spikes are increased, and decreased if vice versa. After such training, the neurons begins to actively react to pre-spikes received from neurons with larger connection weights. This leads to the neuron weights learning certain features (Fig. \ref{fig:training}). If these pre-spikes are recieved in a short enough time period, they might cause a new spike. The opposite rule (with $A_{+}$ and $A_{-}$ having the opposite signs) is called the anti-STDP \parencite{anti-STDP} rule. It is used to train inhibitory connenctions in section \ref{section:competition-training} of this paper.

@@

To answer this question, in order to update the $ YY $ connections, the anti-STDP rule was chosen (the rule opposite in the signs of $ A_{+} $ and $ A_{-} $ to standard STDP). For different values of the parameters of this rule, different distributions of inhibitory weights were obtained. The initial values of the weights were set from a uniform distibution from 0 to a certain negative values. Experiments were carried out with LCSNN networks.

\begin{table}[H]
 \caption{anti-STDP parameters}
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Figure & {$\tau_{+}$, ms} & {$\tau_{-}$, ms} & {$A_{+}$} & {$A_{-}$} \\
\hline
\ref{fig:competition_distributions:weakest}, \ref{fig:worst_competition_distribution} & 14.7 & 14.2 & -0.5 & 1.5 \\
\hline
\ref{fig:competition_distributions:weak}, \ref{fig:medium_bad_competition_distribution} & 5.4 & 15.1 & -1.2 & 0.6 \\
\hline
\ref{fig:competition_distributions:medium}, \ref{fig:medium_good_competition_distribution} & 17.6 & 24.5 & -1.9 & 1.6 \\
\hline
\ref{fig:competition_distributions:strong}, \ref{fig:best_competition_XY} & 17.7 & 16.5 & -0.1 & 1.6\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

During the optimization of the models, the accuracy of a large number of LCSNNs was measured with various hyperparameter configurations (Fig. \ref{fig:hyperparams}). It can be seen that configurations with high accuracy (dark lines) are localized in a manner that encourages negative weight accumulation for larger time differencies $t_{post} - t_{pre}$ between -post and -pre spikes (for the anti-STDP weight update rule).

@@

\caption{Visualization of the achieved LCSNN recognition accuracy when using various combinations in the hyperparameters space. The parameters <<normalization weight>>, <<initial inhibitory weight>> and <<weight decay>> are responsible for the weights values, and the next two parameters are combinations of anti-STDP parameters
}
 \label{fig:hyperparams} 
\end{center} 
\end{figure}

>>>>

Thus, in the process of learning, the weights of connections where pre-spikes are systematicly recieved right before the emmision of post-spikes are increased, and decreased if vice versa. After such training, the neurons begins to actively react to pre-spikes received from neurons with larger connection weights. This leads to the neuron weights learning certain features (Fig. \ref{fig:training}). If these pre-spikes are recieved in a short enough time period, they might cause a new spike. The opposite rule (with $A_{+}$ and $A_{-}$ having the opposite signs) is called the Anti-STDP \parencite{Anti-STDP} rule. It is used to train inhibitory connenctions in section \ref{section:competition-training} of this paper.

@@

To answer this question, in order to update the $ YY $ connections, the Anti-STDP rule was chosen (the rule opposite in the signs of $ A_{+} $ and $ A_{-} $ to standard STDP). For different values of the parameters of this rule, different distributions of inhibitory weights were obtained. The initial values of the weights were set from a uniform distibution from 0 to a certain negative values. Experiments were carried out with LCSNN networks.

\begin{table}[H]
 \caption{Anti-STDP parameters}
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Figure & {$\tau_{+}$, ms} & {$\tau_{-}$, ms} & {$A_{+}$} & {$A_{-}$} \\
\hline
\ref{fig:competition_distributions:weakest}, \ref{fig:worst_competition_distribution} & 14.7 & 14.2 & -0.5 & 1.5 \\
\hline
\ref{fig:competition_distributions:weak}, \ref{fig:medium_bad_competition_distribution} & 5.4 & 15.1 & -1.2 & 0.6 \\
\hline
\ref{fig:competition_distributions:medium}, \ref{fig:medium_good_competition_distribution} & 17.6 & 24.5 & -1.9 & 1.6 \\
\hline
\ref{fig:competition_distributions:strong}, \ref{fig:best_competition_XY} & 17.7 & 16.5 & -0.1 & 1.6\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

During the optimization of the models, the accuracy of a large number of LCSNNs was measured with various hyperparameter configurations (Fig. \ref{fig:hyperparams}). It can be seen that configurations with high accuracy (dark lines) are localized in a manner that encourages negative weight accumulation for larger time differencies $t_{post} - t_{pre}$ between -post and -pre spikes (for the Anti-STDP weight update rule).

@@

\caption{Visualization of the achieved LCSNN recognition accuracy when using various combinations in the hyperparameters space. The parameters <<normalization weight>>, <<initial inhibitory weight>> and <<weight decay>> are responsible for the weights values, and the next two parameters are combinations of Anti-STDP parameters
}
 \label{fig:hyperparams} 
\end{center} 
\end{figure}
